\begin{rubric}{Employment}
\entry*[2023 -- present]%
	\textbf{Postdoctoral Research Fellow.} University of Michigan Physics Department. \linebreak
    \vspace{-1.5em}
    \hspace{-1em}%
    \begin{itemize}
        \setlength\itemsep{0em}
        \setlength{\itemindent}{-10em}
        \item Boosted precision by 70\% with new methods for multi-task learning and message passing in transformers. 
        \item New transformer methods will accelerate the timeline for discovery by 10 years by requiring less data.
        \item Reduced uncertainty in ML predictions by 75\% (to the 3\% level), with novel methods in domain adaptation.
        \item Analyze 100s of millions of GB of data on millions of distributed computing cores in 42 countries.
        %\item Reduced false positives by 80\% through innovative ML research in kernel density estimation.
        %\item Used advanced deep learning techniques (deep sets, pNN) increasing classifier precision from 78\% to 94\%.
        %\item Delivered a data acquisition system with 25k channels by managing a 3 years of hardware integration.
        %\item Developed a software framework for detector calibration which exceeded the target precision by 8\%.
    \end{itemize}
%
\entry*[2024 -- 2025]%
	\textbf{Software engineer, technical lead, group leader.} CERN ATLAS experiment. \linebreak
    \vspace{-1.5em}
    \hspace{-1em}%
    \begin{itemize}
    \setlength\itemsep{0em}
        \setlength{\itemindent}{-10em}
        \item Selected from a competitive pool of 14 nominees to lead critical software modernization.
        \item Accelerated feedback for GB/s data streams from months to hours by automating processing.
        \item Saved estimated \$10M in computing hours with automated framework that flags problems earlier. 
        \item Brought 5 students projects back on schedule ($\approx$12 months) with technical leadership and written feedback.
    \end{itemize}
%
\end{rubric}