% SW grant: 5/14 selected

%-------------------------
% Resume in Latex
% Author : Gabriel Sison
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% allcolors=cyan
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\PassOptionsToPackage{style=ieee,sorting=ydnt,uniquename=init,defernumbers=true}{biblatex}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{settings}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-5pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeNonBullet}[2]{
  \vspace{-5pt} \hspace{1em}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{1pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\PassOptionsToPackage{style=ieee,sorting=ydnt,uniquename=init,defernumbers=true}{biblatex}
\addbibresource{own-bib.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        % NAME
        {\Huge\scshape Kevin Nelson, PhD} 
        % SUBHEADING
        \\ 
        \small
        % phone number
        {\raisebox{-0.2\height}\faPhone\ +1 843 412 0136} ~
        % EMAIL
        \href{mailto:kevin.m.nelson14@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{\smash{kevin.m.nelson14@gmail.com}}} ~ 
        % LINKEDIN
        \href{https://www.linkedin.com/in/kevnels/}{\raisebox{-0.2\height}\faLinkedin\ \underline{\smash{linkedin.com/in/kevnels}}}  ~
        
        % GITHUB
        \href{https://github.com/kmnelson?tab=repositories}{\raisebox{-0.2\height}\faGithub\ \underline{\smash{github.com/kmnelson}}} ~
        % personal site
        \href{https://kmnelson.github.io/portfolio/}{\raisebox{-0.2\height}\faGlobe\ \underline{\smash{kmnelson.github.io}}} ~
        % CV / publications
        \href{https://kenelson.web.cern.ch/kenelson/portfolio/CV_Kevin_Nelson.pdf}{\raisebox{-0.2\height}\faBook\ \underline{\smash{CV/publications}}}
    \end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%% Impact statement %%%%%%%%%%%%%%%%%%%%%%%%%%%% 


Software engineer with specialized expertise in machine learning and AI systems. 
Proven track record of leading cross-functional teams, establishing technical direction, and implementing industry best practices in software development. 
Deep understanding and experience with LLM architectures, fine-tuning, and deployment.
Comprehensive technical knowledge in Python and C++ with a collaborative approach to deliver high-reliability systems that consistently exceed performance metrics.
Highly experienced at scale, in repositories up to 6 million lines of code and in deploying code to millions of distributed cores.

%Demonstrated success in developing and scaling ML models from concept to production, driving measurable business outcomes through innovative technical solutions. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Employment}
    \resumeSubHeadingListStart
        
        % COMPANY 1
        \resumeSubheading{CERN ATLAS Experiment}{Meyrin, Switzerland}{Software Engineer, technical lead}{2024 - 2025}
        \resumeItemListStart
            \resumeItem{Selected from a competitive pool of 14 nominees to lead critical software modernization, complete residency in Meyrin.}
            \resumeItem{As technical lead implemented object-oriented design patterns, pydantic validation, ruff linting, and CI/CD pipelines.}
            \resumeItem{Reduced feedback time for high-volume data streams (2 GB/s) from months to hours by automating data processing.}
            \resumeItem{Saved estimated \$10M in computing hours with automated framework that flags problems earlier.}
        \resumeItemListEnd
        \resumeNonBullet{Reference: \href{mailto:Rosy.Nicolaidou@cern.ch}{\underline{\smash{Dr. Rosy Nikolaidou}}} and \href{mailto:Stylianos.Angelidakis@cern.ch}{\underline{\smash{Dr. Stelios Angelidakis}}}}
        
        \vspace{-1.2em} 
        
        \resumeSubheading{University of Michigan}{Ann Arbor, MI}{Postdoctoral Research Fellow, specializing in AI applications}{2023 - present}
        \vspace{8pt}
        \resumeSubheadingContinue{Graduate student / Doctoral candidate}{2018 - 2023}
        \resumeItemListStart
        \vspace{-4pt}
            \resumeItem{Led 3 technical projects, scaling to analyze 100s of millions of GB on millions of computing cores.}
            \resumeItem{Boosted precision by 70\% with innovative methods for multi-task learning and message passing in transformers.}
            \resumeItem{Developed detector calibration framework exceeding precision targets by 8\%, with automated doxygen documentation.}
            \resumeItem{Authored 40,000+ lines of code in lead projects, with key contributions to a larger 6M+ line codebase.}
        \resumeItemListEnd
        \resumeNonBullet{Reference: \href{mailto:qianj@umich.edu}{\underline{\smash{Prof. Jianming Qian}}}, \href{mailto:amidei@umich.edu}{\underline{\smash{Prof. Dante Amidei}}}{} and \href{mailto:bzhou@umich.edu}{\underline{\smash{Prof. Bing Zhou}}}}{}

    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5em}
\section{Education}
  \resumeSubHeadingListStart
  
    % MAIN INFORMATION
    \resumeSubheading
    {University of Michigan}{Ann Arbor, MI}
    {Ph.D. Physics, Experimental particles and fields, 4.0 /4.0 GPA}{2018-2023}
        % BULLET POINTS
        \resumeItemListStart
            \resumeItem{\textbf{Awards:} Stephanie Zimmerman thesis prize (Best Ph.D. thesis including the muon system).}
        \resumeItemListEnd
    % 5 nominations
    \resumeSubheading
    {The College of William and Mary}{Williamsburg, VA}
    {BS Computer Science, BS Physics, 3.92 / 4.0 GPA}{2014-2018}
        % BULLET POINTS
        \resumeItemListStart
            \resumeItem{\textbf{Awards:} Don Edward Harrison Jr. Award (Top Physics undergraduate student).}
        \resumeItemListEnd
        % approx. 30 students
  \resumeSubHeadingListEnd
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1em}
\section{Projects (Personal + Professional open source)} 
    \resumeSubHeadingListStart

        % Project 2
        \resumeProjectHeading
        {KDE for differentiable test statistics -\href{https://github.com/kmnelson/functional-decomposition}{\raisebox{-0.2\height}\ \underline{\smash{functional-decomposition}}}}
        % Date
        {February 2025}
        \resumeItemListStart
            \resumeItem{Increased speed of bottlenecked tasks by 10x by porting code to GPUs.}
            \resumeItem{Extended ML density estimation technique to NN outputs, allowing for differentiable p-values.}
        \resumeItemListEnd
        
        % Project 1

        \resumeProjectHeading
        {LLM Sarcasm Detection Fine-Tuning -\href{https://kmnelson.github.io/sarcasm/}{\raisebox{-0.2\height}\ \underline{\smash{sarcasm}}}}
        % Date
        {April 2025}
        \resumeItemListStart
            \resumeItem{Fine-tune BERT to detect sarcasm with F1-score of 0.975 on The Onion vs. news headlines.}
            \resumeItem{Improve generalization accuracy by 10\% without sacrificing validation set performance by weighting by feature frequency.}
        \resumeItemListEnd  
\vspace{-10pt}
        \resumeProjectHeading{Simulation of Future Particle Detector - \href{https://gitlab.cern.ch/kenelson/fcc-straw-tracker}{\raisebox{-0.2\height}\ \underline{\smash{fcc-straw-stracker}}}}{May 2024}
        \resumeItemListStart
            \resumeItem{Help steer 20 year plan to build \$20B experiment by simulating different machine layouts.}
            \resumeItem{Serve as technical lead, advising students and enforcing code linting, CI/CD, review MRs.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Technical Skills  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-13pt}
\section{Technical Skills}
    \vspace{-7pt}
    \begin{itemize}
    [leftmargin=0.15in, label={}]{\item{
        % LANGUAGES
        \textbf{Languages}{: python (advanced), C/C++ (advanced), bash (proficient), \LaTeX (proficient), Javascript} \\
        % TOOLS
       \textbf{Machine Learning}{: Transformers, Graph Networks, Deep Learning, Domain Adaptation, Multi-task Learning} \\
       \textbf{Mathematics \& Statistics}{: Kernel Density Estimation, Uncertainty Quantification, Statistical Modeling} \\
        \textbf{Tools \& Infrastructure}{: Docker, CMake, CI/CD Pipelines, Distributed Computing}\\
        }}
    \end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Publications  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Publications and Presentations}
%\nocite{*}
%\printbibliography[heading={subbibliography},title={Journal Articles},type=article]
%\printbibliography[heading={subbibliography},title={Talks and Posters},type=inproceedings]



\end{document}
